The hydra and the rooster

### 2020-08-06 latex/chapter-ks.tex
corrections on pdf file

\begin{Coqsrc}
Class BoundedVariant  (B:Battle) :=
  {
    mu:T1 ;
    m: Hydra -> T1;
    mu_nf : nf mu;
    Hvar : Hvariant T1_wf B m;
    m_bounded : forall h, m h < mu
  }.
\end{Coqsrc}

@@

In the mathematical text and figures, we shall use the notation 
$\alpha \xrightarrow[i,j]{}\beta$ for the proposition 
\texttt{standard\_path $i$ $\alpha$ $j$ $\beta$}.
In~\cite{KS81} the notation is
$\alpha \xrightarrow[i]{*}\beta$
for 
the proposition  $\exists j, i<j \wedge \alpha \xrightarrow[i,j]{} \beta$.

@@

 \begin{enumerate}
 \item $\alpha \xrightarrow n \canonseq{\alpha}{n}$
 \item $\canonseq{\alpha}{n} \xrightarrow[1]{} \canonseq{\alpha}{i}$ (by \texttt{Theorem\_2\_4}),
\item $\canonseq{\alpha}{n} \xrightarrow[n]{} \canonseq{\alpha}{i}$ (applying the induction hypothesis to the preceding path);
\item $\canonseq{\alpha}{i} \xrightarrow[n]{} \beta$ (applying the induction hypothesis)\item $\alpha \xrightarrow[n]{} \beta$ (by composition of 1, 3, and 4).

@@

\begin{Coqsrc}
  Compute standard_fun 2 omega 15.
(*   = zero
     : T1 *)
Compute pp (standard_gnaw 2 (omega^omega)  10).
(*
= (omega + 7)%pT1
     : ppT1
*)
Compute pp (standard_gnaw 4 (omega^omega)  100).
(*
 = (omega ^ 3 * 4 + omega ^ 2 * 5 + omega * 3 + 39)%pT1
     : ppT1 *)
\end{Coqsrc}

@@

Since comparison on \texttt{T1} is decidable, one can compute the last step $\gamma$ of the standard path from $(\alpha,n+1)$  such that $\beta\leq \gamma$.
Let $l$ be the length of the path from $\alpha$ to $\gamma$.

% We use for that purpose a function that computes the first index $i$ where $n\leq i <p$ and $P(i+1)$ is
% \texttt{false}, assuming that $P(n)=\texttt{true}$ and $P(p)=\texttt{false}$.

% \begin{Coqsrc}
% first_toggle  (P : nat -> bool) (n p : nat) :
% (n < p)%nat -> P n = true -> P p = false ->
% {l : nat | (n <= l)%nat /\ (l < p)%nat /\
%      (forall i : nat, (n <= i)%nat -> (i <= l)%nat -> P i = true) /\
%       P (S l) = false}
% \end{Coqsrc}

% \begin{Coqsrc}
% Let P (i:nat) := le_b beta (standard_fun (S n) alpha i).

% Remark Rem2 : {t: nat | standard_fun (S n) alpha t < beta}.

% Let t := proj1_sig Rem2.
%  Remark Rem04 : P 0.

% Remark Rem05 : P t = false.

% Remark Rem06 : (0 <  t)%nat.

%  Let l_def :=  first_toggle P 0 t  Rem06 Rem04 Rem05.

% Let l := proj1_sig Rem07.

% Let gamma := standard_fun (S n) alpha l.
% \end{Coqsrc}

This step of the proof is illustrated in figure~\vref{fig:belle-preuve-2}.

@@

In the same way as for free battles, we import a large inequality from 
the module \url{../src/html/hydras.Hydra.Epsilon0_Needed_Generic.html} .

@@

\paragraph*{Proof:} Let us recall that $\texttt{big\_h} = \iota(\mu)$
 and $\texttt{small\_h} = \iota (m (\texttt{big\_h}))$.

@@

In other words, its type should be \texttt{nat -> Hydra -> T1}, and it must 
verify the inequality $m\, (S\,i)\, h' < m\,i\, h$ whenever the configuration 
$(i,h)$ is reachable from some initial configuration $(0,h_0)$
and \texttt{h} is transformed into \texttt{h'} in the considered round.

Can we still prove the theorems of section~\ref{std-case} with this new definition?

>>>>

\begin{Coqsrc}
Class BoundedVariant (B:Battle) :=
  {
    mu:T1 ;
    m: Hydra -> T1;
    mu_nf: nf mu;
    Hvar: Hvariant T1_wf B m;
    m_bounded: forall h, m h < mu
  }.
\end{Coqsrc}

@@

In the mathematical text and figures, we shall use the notation 
$\alpha \xrightarrow[i,j]{}\beta$ for the proposition 
(\texttt{standard\_path $i$ $\alpha$ $j$ $\beta$}).
In~\cite{KS81} the notation is
$\alpha \xrightarrow[i]{*}\beta$
for 
the proposition  $\exists j, i<j \wedge \alpha \xrightarrow[i,j]{} \beta$.

@@

 \begin{enumerate}
 \item $\alpha \xrightarrow[n]{} \canonseq{\alpha}{n}$
 \item $\canonseq{\alpha}{n} \xrightarrow[1]{} \canonseq{\alpha}{i}$ (by \texttt{Theorem\_2\_4}),
\item $\canonseq{\alpha}{n} \xrightarrow[n]{} \canonseq{\alpha}{i}$ (applying the induction hypothesis to the preceding path);
\item $\canonseq{\alpha}{i} \xrightarrow[n]{} \beta$ (applying the induction hypothesis)\item $\alpha \xrightarrow[n]{} \beta$ (by composition of 1, 3, and 4).

@@

\begin{Coqsrc}
  Compute standard_gnaw 2 omega 15.
(*   = zero
     : T1 *)
Compute pp (standard_gnaw 2 (omega^omega)  10).
(*
= (omega + 7)%pT1
     : ppT1
*)
Compute pp (standard_gnaw 4 (omega^omega)  100).
(*
 = (omega ^ 3 * 4 + omega ^ 2 * 5 + omega * 3 + 39)%pT1
     : ppT1 *)
\end{Coqsrc}

@@

Since comparison on \texttt{T1} is decidable, one can compute the last step $\gamma$ of the standard path from $(\alpha,n+1)$  such that $\beta\leq \gamma$.
Let $l$ be the length of the path from $\alpha$ to $\gamma$.  
This step of the proof is illustrated in figure~\vref{fig:belle-preuve-2}.

@@

In the same way as for free battles, we import a large inequality 
from 
the module \href{../src/html/hydras.Hydra.Epsilon0_Needed_Generic.html}{Hydra.Epsilon0\_Needed\_Generic}.

@@

\paragraph*{Sketch of proof:} Let us recall that $\texttt{big\_h} = \iota(\mu)$
 and $\texttt{small\_h} = \iota (m (\texttt{big\_h}))$.

@@

In other words, its type should be \texttt{nat -> Hydra -> T1}, and it must 
verify the inequality $m\, (S\,i)\, h' < m\,i\, h$ whenever the configuration 
$(i,h)$ is reachable from some initial configuration $(0,h_0)$
and \texttt{h} is transformed into \texttt{h'} in the considered round.
Can we still prove the theorems of section~\ref{std-case} with this new definition?
